Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
new v old

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- union(make_ring(7), make_star(7, center = 1, mode = "undirected"))
   g10 <- g10 + edge(2,7)
   plot(g10)

```

@@

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(12345)
   b <- connect.caves(c = 4, nc = 4, n = 20)
   c <- lapply(b, distinction.new, norm = FALSE)
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      c <- c(rep("tan2", n))
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      #ylim(-4, 3.5) + xlim(-4, 3.25) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
```

>>>>

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- union(make_ring(7), make_star(7, center = 1, mode = "undirected"))
   g10 <- g10 + edge(2,7)
```

@@

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(12345)
   b <- connect.caves(c = 4, nc = 4, n = 20)
```

```{r}
   source(here("Functions", "distinction.new.R"))
   distinction(g1)
   distinction.new(g1, norm = TRUE)
```

```{r}
   c <- lapply(b, distinction.new, norm = FALSE)
```

```{r}
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      c <- c(rep("tan2", n))
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      #ylim(-4, 3.5) + xlim(-4, 3.25) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
```
